---
title: "covid19 Viewer Shiny App"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{covid19 Viewer Shiny App}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(covid19ViewerShiny)
```


### How to use `Covid-19 view`

This App is used to monitor global covid-19 cases and deaths, and it can compare the covid-19 cases in different countries.

There are four tabs: `Map`, `Table`, `Graphs`, and `About.

* `Map`: This tab has two leaflet maps. The first one shows the global `cumulative_cases`. The second one shows the global `cumulative_deaths`. Because the dataset contains huge amount of values, the leaflet maps take much time to run. So, please be patient.
* `Table`: This tab shows the latest covid-19 `new_cases`, `cumulative_cases`, `new_deaths`, and `cumulative_deaths` of selected countries. User can select multiple countries to compare them.
* `Graphs`: There are one column plot and one line plot in this tab. The column plot help user compare the latest `cumulative_cases` and `cumulative_deaths` of selected countries. The line plot tells user the `new_cases` and `new_deaths` of selected countries. With these two plots, user can understand how successful selected countries control the coronavirus pandemic.
* `About`: This tab has short introduction about `Covid-19 viewer` and its creator. It also contains the `Acknowledgments` and `References` sections.

```{r info, echo = FALSE}
sessionInfo(package = c("shiny", "readr", "tidyverse", "plotly", "gridExtra", "shinyWidgets", "leaflet", "leaflet.providers", "ggplot2"))
```

