---
title: "covid19 Viewer Shiny App"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{covid19 Viewer Shiny App}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

### How to use `Covid-19 viewer`

```{r setup}
library(covid19ViewerShiny)
```




After `library(covid19ViewerShiny)`, user only need to enter `launch_app()` to run the Shiny app.

The app will be slowly reloaded because of the large size of `covid` dataset. So, please be patient and give it some time.

### About the tabs inside the Shiny app

This App is used to monitor global covid-19 cases and deaths, and it can compare the covid-19 cases in different countries.

There are four tabs: `Map`, `Table`, `Graphs`, and `About.

* `Map`: This tab has two leaflet maps. The first one shows the global `cumulative_cases`. The second one shows the global `cumulative_deaths`. Because the dataset contains huge amount of values, the leaflet maps take much time to run. So, please be patient.
* `Table`: This tab shows the latest covid-19 `new_cases`, `cumulative_cases`, `new_deaths`, and `cumulative_deaths` of selected countries. User can select multiple countries to compare them.
* `Graphs`: There are one column plot and one line plot in this tab. The column plot help user compare the latest `cumulative_cases` and `cumulative_deaths` of selected countries. The line plot tells user the `new_cases` and `new_deaths` of selected countries. With these two plots, user can understand how successful selected countries control the coronavirus pandemic.
* `About`: This tab has short introduction about `Covid-19 viewer` and its creator. It also contains the `Acknowledgments` and `References` sections.

### How to use the Shiny app

User can simply move the slide bars in the app and select different countries. The plot will change according to your selection (except two column plots in the `Graph` tab, they are fixed).

